Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-11 report/report.tex
Update intro to analysis section

Now that the colliison metrics have been obtained, conclusions may be drawn about the technical feasibility of 3D city reproduction from OSM data.
First the geodata precision study will be discussed.
The outcome of that study will be used to assess the quality of the positional accuracy estimate by looking at the dataset completeness, the low semantic accuracy and the unique characteristics of the Stockholm area.
Secondly the collision study will be discussed.
The main outcome is that footpaths will not be more problematic than other road types in city reproduction from OSM data.
This claim will be motivated with the data obtained in section 6.1.
Finally, the character of the feature collision cases will be discussed and the most common cases will be identified.
The chapter will conclude with a presentation of geometrical algorithms for how to correct each case automatically.
For conclusions about the usage of OSM city reproduction in engineering practise and remaining challenges, see section 7.

>>>>

Now that the colliison metrics have been obtained, conclusions may be drawn about the technical feasibility of 3D city reproduction from OSM data.
First the geodata precision study will be discussed.
The outcome of that study will be used to assess the quality of the positional accuracy estimate by looking at the dataset completeness, the low semantic accuracy and the unique characteristics of the Stockholm area.
Secondly the collision study will be discussed.
The main outcome is that footpaths will not be more problematic than other road types in city reproduction from OSM data.
This claim will be motivated with the data obtained in section 4.1.
Finally, the character of the feature collision cases will be discussed and the most common cases will be identified.
The chapter will conclude with a presentation of geometrical algorithms for how to correct each case automatically.
For conclusions about the usage of OSM city reproduction in engineering practise and remaining challenges, see section 5.
